Predicting the effects of character displacement on food-web dynamics

### 2019-02-06 manuscript_ECD_model.Rmd
edited end of 2nd paragraph in intro to better tie in rationale for a food-web perspective.

Although explicit models of resources gave insights to the evolution of character displacement, the ecological feedback onto consumer-resource dynamics have received surprisingly little attention. This is likely because the ecological feedback has been primarily studied through the lens of competition and coexistence theory [Lawlor1976; Germain2018; Bassar; McPeek]. For example, early theoretical work by @Lawlor1976 showed that ecological character displacement promotes coexistence by favoring specialized consumers that experience reduced interspecific competition. On the other hand, specialization often increases a consumer’s ability to capture a specific resource. A well known consequence of increased foraging efficiency is resource suppression, which if sufficient enough, can generate oscillations, and hence less stable, consumer-resource dynamics [Rosenzweig 1971; Murdoch et al. 2003; McCann 2011]. NEED A LAST SENTENCE TO WRAP IT UP, HIGHLIGHTING HOW A FOOD-WEB PERSPECTIVE MAY YIELD NEW ECOLOGICAL INSIGHTS AND GIVE A CONTRASTING PERSPECTIVE TO COEXISTENCE THEORY. PERHAPS A I NEED TO INCLUDE A SENTENCE MID-WAY THROUGH SUGGESTING THAT A FOOD-WEB PERSPECTIVE MAY GIVE QUALITATIVELY DIFFERENT INSIGHTS. IT MAY BE NICE TO BRING IN THE SPATIAL COUPLING WORK OF MCCANN SUGGESTING THAT SPECIALIZATION CAN COUPLE FOOD-WEBS, BUT THIS WAS ONLY WITH ONE TOP PREDATOR (I.E. NO CONSUMERS...LOOK AT OLD TEXT FOR WORDING SUGGESTIONS.)

>>>>

Although explicit models of resources gave insights to the evolution of character displacement, the ecological feedback onto consumer-resource dynamics have received surprisingly little attention. 
This is likely because the ecological feedback has been primarily studied through the lens of competition and coexistence theory [Lawlor1976; Germain2018; Bassar; McPeek]. 
For example, early theoretical work by @Lawlor1976 showed that ecological character displacement promotes coexistence by favoring specialized consumers that experience reduced interspecific competition. 
<!--
On the other hand, specialization often increases a consumer’s ability to capture a specific resource.
From food-web theory, we know that increased feeding rates often lead to resource suppression, which if sufficient enough, can generate oscillations, and hence less stable, consumer-resource dynamics [Rosenzweig 1971; Murdoch et al. 2003; McCann 2011].
-->
Yet, this reduction in interspecific competition may, at the same time, increase the interspecific interaction between a consumer and the resource it specializes on.  
Both food-web theory and empirical studies have shown that increasing the strength of consumer-resource interactions often leads to resource suppression, which if sufficient enough, can generate oscillations, and hence less stable consumer-resource dynamics [@Rosenzweig1971; @Luckinbill1973; @Murdoch2002; @Murdoch2003; @McCann2011].
Thus, a food-web perspective, which accounts for both the direct and indirect effects of consumer-resource interactions, may yield new insight to the ecological consequences of character displacement.

<!--Thus, a consumer-resource perspective may yield new insight to the ecological feedback of character displacement on food-web dynamics. 
<!--Given that character displacement is mediated by a consumer-resource interaction, a food-web perspective may yield   NEED A LAST SENTENCE TO WRAP IT UP, HIGHLIGHTING HOW A FOOD-WEB PERSPECTIVE MAY YIELD NEW ECOLOGICAL INSIGHTS AND GIVE A CONTRASTING PERSPECTIVE TO COEXISTENCE THEORY. PERHAPS A I NEED TO INCLUDE A SENTENCE MID-WAY THROUGH SUGGESTING THAT A FOOD-WEB PERSPECTIVE MAY GIVE QUALITATIVELY DIFFERENT INSIGHTS. IT MAY BE NICE TO BRING IN THE SPATIAL COUPLING WORK OF MCCANN SUGGESTING THAT SPECIALIZATION CAN COUPLE FOOD-WEBS, BUT THIS WAS ONLY WITH ONE TOP PREDATOR (I.E. NO CONSUMERS...LOOK AT OLD TEXT FOR WORDING SUGGESTIONS.)-->
